---
title: "Lab 00 - Hello IDS!"
author: "Matthew W"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Matthew", "Matt", 
           "Julian"),
  github_username = c("mcgregors-garden", "mthw2304", "mw-mw-mw5051", 
                      "Julianlee007"), 
  colour = c("powderblue", "#6b4bed", "dark green", 
             "aquamarine"),
  hobby = c("Hopping", "Board Games", "movies", 
            "football"),
  favourite_number = c(2, 3.141592653589793238462643383279502884197169, 5, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar graph of teams favourite numbers, labelled with github usernames, bars are the favourite colours.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github username", 
          y = "favourite number",
          title = "Team favourite numbers")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The bar chart does not work very well as the topic (favourite hobby) lends itself to a wide range of answers with low counts. This leads to a display of many short bars that are hard to interpret. The data would be easier to read with a pie chart as it will show the proportion of people with each hobby.
